Toward Resolved Simulations of Burning Fronts in Thermonuclear X-ray Bursts

### 2018-09-26 astronum_2018/astronum-xrb.tex
more discussion of cost

\section{Estimates for Full Star Simulations}

A fully resolved calculation of burning over the entire neutron star
is out of reach, and will be for some time.

time estimate...

\MarginPar{Alice and Mike will work on this}

\section{Algorithmic Developments}

>>>>

\section{Large Scale Simulations and Algorithmic Developments}

The 2D calculations shown in the previous section require about 10k
node-hours of computational time to get to about 10~ms (those
particular simulations were run at NERSC).  The GPU version of the
Castro hydrodynamics solver, under active development, is about
$10\times$ faster on a comparable node, so a GPU calculation could
bring the 2D cost down to 1k node-hours.  Most of this time is spent
in the reactions\MarginPar{verify fraction}.  A 3D version of this
calculation is estimated to require 5M node-hours on CPUs or 0.5M
node-hours using GPUs---this is about the size of an
annual \MarginPar{double check \#s} allocation.  Additionally, this is
still with the boosted flame, but we expect that once the flame is
developed, the boosting will not be as critical, due to hydrodynamic
effects.  We plan to test this soon.  In any case, this is less than
1\% of the neutron star surface, so a fully resolved calculation of
burning over the entire neutron star is out of reach, and will be for
some time.
